[Result, but poetic]: Does LLM Use Improve Data Science Education?

### 2024-08-01 paper/paper.qmd
finished ai_appropriateness sentiment

library(tidyverse)
library(knitr)
library(kableExtra)
library(lintr)
library(tidyr)
library(tidytext)
library(textdata)
library(quanteda)

@@

@@

```{r fig-AI-helpfulness}
#| message: false
#| echo: false
#| warning: false
#| fig-cap: How Students Use ChatGPT
#| fig-align: center

@@

#get positive words from NRC lexicon
pos_words <- get_sentiments("nrc") |>
  filter(sentiment = c("anger", "disgust", "fear", "negative", "sadness"))

#get negative words from NRC lexicon
neg_words <- get_sentiments("nrc") |>
  filter(sentiment = c("joy", "positive",
"surprise",
"trust", 
"anticipation"))
```

We then performed sentiment analysis on the free-response comment questions asked to students. To perform this text analysis, the tidytext package [@tidytext] was used in conjunction with the NRC word-emotion lexicon compiled by @mohammad. Although four lexicon options were available in tidytext, the NRC lexicon was chosen due to the relatively balanced amounts of positive and negative words in the dataset, allowing for balanced classification.

@@

```{r setup-ai-appropriate}

@@

>>>>

library(tidyverse)
library(knitr)
library(kableExtra)
library(lintr)
library(tidyr)
library(tidytext)
library(textdata)
library(wordcloud)
library(reshape2)

@@

```{r fig-boilerplate}
#| message: false
#| echo: false
#| warning: false
#| fig-cap: (CHANGE) Boilerplate figure caption 
#| fig-align: center
# survey_data |>
#   ggplot(program_counts, aes(x = "", y = n, fill = program_of_study)) +
#   #put geom type here (put before compilation) +
#   labs(title = "Title!",
#        x = "X label",
#        y = "Y label") +
#   theme_minimal() +
#   scale_fill_discrete(name="Legend Title") +
#   theme(plot.title.position = "plot",
#         plot.title = element_text(hjust = 0.5)
#         )
```

```{r tbl-boilerplate}
#| message: false
#| echo: false
#| warning: false
#| tbl-cap: (CHANGE) Boilerplate table caption 
#| fig-align: center
#Put code below this line
```

@@

```{r fig-AI-helpfulness}
#| message: false
#| echo: false
#| warning: false
#| fig-cap: CHANGE/REMOVE
#| fig-align: center

@@

#get positive words from NRC lexicon
neg_words <- get_sentiments("bing") |>
  filter(sentiment == "negative")

#get negative words from NRC lexicon
pos_words <- get_sentiments("bing") |>
  filter(sentiment == "positive")
```

We then performed sentiment analysis on the free-response comment questions asked to students. To perform this text analysis, the tidytext package [@tidytext] was used.

@@

```{r setup-ai-appropriate}
#| message: false
#| echo: false
#| warning: false

@@

```{r tbl-ai-appropriate}
#| message: false
#| echo: false
#| warning: false
#| tbl-cap: Comparing Incidences of Positive and Negative Words.
#| tbl-subcap: ["Top 10 Mentioned Positive Words", "Top 10 Mentioned Negative Words"]
#| layout-ncol: 2
#| fig-align: center

# Generate positive words table
tbl_ai_pos <- tidy_ai_comments |>
  ungroup() |>
  select(-c("id")) |>
  inner_join(pos_words) |>
  count(word, sort = TRUE) |>
  head(10) |>
  kable(, format = "markdown")

# Generate negative words table
tbl_ai_neg <- tidy_ai_comments |>
  ungroup() |>
  select(-c("id")) |>
  inner_join(neg_words) |>
  count(word, sort = TRUE) |>
  head(10) |>
  kable(, format = "markdown")

tbl_ai_pos
tbl_ai_neg

```{r fig-wordcloud-ai-appropriate}
#| message: false
#| echo: false
#| warning: false
#| fig-cap: (CHANGE) Boilerplate figure caption 
#| fig-align: center

# Load sentiment lexicon
sentiments <- get_sentiments()

# Prepare data for comparison cloud
comparison_data <- tidy_ai_comments |>
  inner_join(sentiments) |>
  count(word, sentiment, sort = TRUE) |>
  acast(word ~ sentiment, value.var = "n", fill = 0)

# Generate comparative word cloud
comparison.cloud(
  comparison_data,
  colors = c("darkred", "darkgreen"),
  max.words = 100,
  title.size = 1.5,
  scale = c(3, 0.5)  # Adjust scale for word size
)
